---
title: "Societal Fragility Dashboard"
subtitle: "2024 IOM South Sudan"
author: "Data & Methods Subteam - Bass Connections"
date: "2024-09-29"
output:
 html_document:
   theme: journal
   toc: true
   toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(ggthemes)
library(readxl)
library(purrr)
library(janitor)
library(forcats)
library(scales)
library(knitr)
library(kableExtra)

library(sjmisc)
library(likert)
library(writexl)

options(digits=2)
```

```{r data, include=FALSE}

# Setting up directory

main_data_df <- read.csv("data/Bass_Team_Data_V2.csv")

```

```{r}
#CODE STARTS AFTER THIS BLOCK
```

# 5) Societal Fragility

```{r societal_data}
# colnames(main_data_df)

soc_index_df <- main_data_df %>% 
                select("Q1.5_County", 
                       "Q6.1_raw", "Q6.2_raw", "Q6.3_raw", "Q6.4_raw", "Q6.9_raw", 
                       "Q6.1_unimputed", "Q6.2_unimputed", "Q6.3_unimputed", "Q6.4_unimputed", "Q6.9_unimputed")

# colnames(soc_index_df)
```

All the answers are in a **scale of 0-1**, i.e. can have the following values: 0, 0.25, 0.5, 0.75, 1. The higher, the more fragile.

The higher, the more fragile.

Ex:
0 = Not severe at all 
0.25 = Not severe
0.50 = Somewhat severe
0.75 = Severe
1 = Extremely severe

## Index Questions

### Q6.1 How much do you feel welcomed or accepted in your current community? {.tabset}

#### Entire sample

```{r Q6.1, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  summarize(mean = mean("Q6.1_unimputed", na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.1_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q6.1_raw, answers) %>%
  mutate(percentage = answers/sum(answers) * 100) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.1_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q6.1_raw, answers) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q6.1_raw = factor(Q6.1_raw)) %>%
  ggplot(aes(Q6.1_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q6.1_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q6.1 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q6.1_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q1.5_County, Q6.1_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers) * 100) %>%
  ungroup() %>%
  select(Q1.5_County, Q6.1_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

### Q6.2 In the past year, how often, if at all, have you been personally discriminated against based on any of the following: your gender, your religion, your ethnicity, any disability you might have, or your place of origin?

#### Entire sample

```{r Q6.2, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  summarize(mean = mean(Q6.2_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.2_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q6.2_raw, answers) %>%
  mutate(percentage = answers/sum(answers) * 100) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.2_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q6.2_raw, answers) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q6.2_raw = factor(Q6.2_raw)) %>%
  ggplot(aes(Q6.2_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q6.2_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q6.2 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q6.2_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q1.5_County, Q6.2_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers) * 100) %>%
  ungroup() %>%
  select(Q1.5_County, Q6.2_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

### Q6.3 To what extent do you agree with the following statement? “People in your boma are willing to help each other.”

#### Entire sample

```{r Q6.3, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  summarize(mean = mean(Q6.3_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.3_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q6.3_raw, answers) %>%
  mutate(percentage = answers/sum(answers) * 100) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.3_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q6.3_raw, answers) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q6.3_raw = factor(Q6.3_raw)) %>%
  ggplot(aes(Q6.3_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q6.3_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q6.3 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q6.3_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q1.5_County, Q6.3_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers) * 100) %>%
  ungroup() %>%
  select(Q1.5_County, Q6.3_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

### Q6.4 Imagine that you were in an argument with your neighbor about a small issue. To what extent do you agree or disagree with the following statement? “I know who I could seek help from to resolve this argument.”

```{r Q6.4, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  summarize(mean = mean(Q6.4_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.4_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q6.4_raw, answers) %>%
  mutate(percentage = answers/sum(answers) * 100) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.4_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q6.4_raw, answers) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q6.4_raw = factor(Q6.4_raw)) %>%
  ggplot(aes(Q6.4_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q6.4_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```

#### By county

```{r Q6.4 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q6.4_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q1.5_County, Q6.4_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers) * 100) %>%
  ungroup() %>%
  select(Q1.5_County, Q6.4_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

### Q6.9 How would you describe the relationship between individuals who are not originally from the community and the rest of the community members?

```{r Q6.9, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  summarize(mean = mean(Q6.9_unimputed, na.rm = TRUE)) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.9_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(answers)) %>%
  select(Q6.9_raw, answers) %>%
  mutate(percentage = answers/sum(answers) * 100) %>%
  kable(align = "lc", 
        col.names = c("Response", "Number of Responses", "Percent of Total Responses")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q6.9_raw) %>%
  summarise(answers = n()) %>%
  arrange(desc(-answers)) %>%
  select(Q6.9_raw, answers) %>%
  mutate(percentage = answers / sum(answers) * 100,
         Q6.9_raw = factor(Q6.9_raw)) %>%
  ggplot(aes(Q6.9_raw, answers)) +
  geom_col( fill = "blue", color = "black", alpha = 0.7) +
  labs(x = "Q6.9_raw", y = "Number of respondents") +
  theme(axis.text.x = element_text(size = 11),
        axis.title.x = element_text(margin = margin(t = 10))) +
  coord_flip() 

```
#### By county

```{r Q6.9 by county, eval = TRUE, warnings = FALSE, echo = FALSE, message = FALSE, out.width="65%"}

soc_index_df %>% 
  group_by(Q1.5_County) %>% 
  summarize(mean = mean(Q6.9_unimputed, na.rm = TRUE)) %>% 
  kable(align = "lc", col.names = c("County", "Mean Response (0 to 1)")) %>%
  kable_styling(position = "left", full_width = F)

soc_index_df %>%
  group_by(Q1.5_County, Q6.9_raw) %>%
  summarise(answers = n(), .groups = 'drop') %>%
  arrange(desc(Q1.5_County)) %>%
  group_by(Q1.5_County) %>%
  mutate(percentage = answers / sum(answers) * 100) %>%
  ungroup() %>%
  select(Q1.5_County, Q6.9_raw, answers, percentage) %>%
  kable(align = "lc") %>%
  kable_styling(position = "left", full_width = F)

```

## Additional Questions

Coming soon...

